---
title: "Analysis of DevBots"
css: ./rmarkdown_resources/tables_format.css
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    df_print: paged
  html_document:
    toc: yes
    df_print: paged
bibliography: ./rmarkdown_resources/packages.bib
---

# Analysis of DevBots

```{r installing, include=FALSE}
# Uncomment this line in order to install all required packages.
#install.packages(c("tidyverse","viridis","gridExtra", "ggrepel"))
```

```{r setup, include=FALSE}
#List of library dependencies
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)  # Package for data wrangling and plotting.
library(ggrepel)    # Package for better layout of labels in plots.
library(viridis)    # Package for the colors used in the chart
library(kableExtra) # Package to render tables that look nicer.

# Here, we simply create a bib file to reference all packages we are using in this script.
knitr::write_bib(c("tidyverse", "gridExtra", "kableExtra"), 
                 file = "./rmarkdown_resources/packages.bib")

#Color-blind friendly palette with 7 values.
cbbPalette <- c("#CC79A7", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#000000")

# A default theme for the PLOTS
PLOT_THEME <- theme_minimal(base_size = 10) + 
  theme(plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
        panel.grid.minor = element_blank(),legend.position = "bottom", 
        axis.line = element_line(size = 1), axis.ticks = element_line(size = 1),
        strip.background = element_rect(colour = "white", fill = "aliceblue"))

# Path to folders with DevBots projects
BOT_CSV_PATH <- "../ruby/watchers/"
# Names of the devbots TODO: Change this to automatically parsing filenames.
bot_names <- c("imgbot","snyk","pyup","whitesource","greenkeeper","dependabot","renovate")
```

```{r, echo=FALSE, message=FALSE,cache=TRUE}
# --------------------------------------------------------------------
# Data cleaning and processing
# Goes through all files and build a big DataFrame with all bots.
# --------------------------------------------------------------------
all_bots_df <- data.frame()
for(bot_name in bot_names){
  bots_df <- read.csv2(paste(BOT_CSV_PATH,bot_name,".csv",sep=""),header = TRUE, sep= ";")
  bots_df <- bots_df %>% filter(is_forked == "false") %>%  
    mutate("BotName" = bot_name)
    
  all_bots_df <- bind_rows(all_bots_df, bots_df)
}
```

## Tables

Showing some of the tables that we generated:

```{r, echo = FALSE}
projects_per_bot <- all_bots_df %>% 
  group_by(BotName) %>% 
  tally(name = "TotalProjects") %>% 
  mutate(Perc = round(100*TotalProjects/nrow(all_bots_df),2)) %>% 
  arrange(-TotalProjects)
knitr::kable(projects_per_bot, longtable = T, digits = 3,
             caption = "Number of projects per each DevBot") %>% 
  kable_styling(bootstrap_options = c("hover","striped","responsive","condensed")) %>% 
  scroll_box(width = "100%", height = "200px")
```

Table that shows which projects have more than one DevBot. Its ordered in a descending order on projects with more DevBots.

```{r, echo = FALSE}
multibot_projects_df <- all_bots_df %>% 
  group_by(project) %>% 
  mutate(ListDevBots = paste0(BotName, collapse = ",")) %>% 
  group_by(project, ListDevBots) %>% 
  tally(name = "NumOfDevBots") %>% 
  filter(NumOfDevBots > 1) %>% 
  arrange(-NumOfDevBots) %>% 
  select(project, NumOfDevBots, ListDevBots)

knitr::kable(multibot_projects_df, longtable = T, digits = 3,
             caption = "Projects that include more than one DevBot (descending order).") %>% 
  kable_styling(bootstrap_options = c("hover","striped","responsive","condensed")) %>% 
  scroll_box(width = "100%", height = "200px")
```

Table that shows the proportion of multiple bots in different projects. For instance: X% of the projects have 3 bots
```{r, echo = FALSE}
multibot_summary_df <- multibot_projects_df %>% 
  group_by(NumOfDevBots) %>% count(NumOfDevBots, name = "Count") %>% 
  mutate(Perc = round(100*Count/nrow(multibot_projects_df),2))

knitr::kable(multibot_summary_df, longtable = T, digits = 3,
             caption = "Proportion of multiple bots in different projects.") %>% 
  kable_styling(bootstrap_options = c("hover","striped","responsive","condensed")) %>% 
  scroll_box(width = "100%", height = "200px")
```

## Some plots:                     

Shows the names of the bots with more than 500 watchers and subscribers

```{r, echo = FALSE, warning=FALSE}
# TODO: Rethink this plot, too crowded with information. Table better?!
plot_popularity <- ggplot(all_bots_df, aes(x = subscribers, y = watchers)) + 
  geom_point(alpha = 0.25, aes(color = BotName)) + 
  scale_fill_manual(values = cbbPalette) +
  geom_label_repel(data = filter(all_bots_df, watchers>500 & subscribers > 500),aes(label=project), max.overlaps = ) +
  PLOT_THEME +
  facet_wrap(~BotName, ncol = 4, scales = "free")
plot_popularity
```



```{r, echo = FALSE, warning=FALSE}
#Histogram of the distribution of watchers.
# TODO:  Not good, because too many projects have few watchers.Fix this one.
# Removed this plot from HTML because it takes too long to render
#plot_watch_histogram <- ggplot(all_bots_df, aes(x = watchers)) + 
#  geom_histogram(binwidth = 100) + 
#  facet_wrap(~BotName, ncol = 4, scales = "free") + 
#  PLOT_THEME
```

```{r, echo = FALSE, warning=FALSE}
# Donut chart, but without the % values (TODO: add lab position column and then geom_text)
donut_plot <- ggplot(projects_per_bot, aes(x = 2, y = Perc)) + geom_bar(stat= "identity", color = "white", aes(fill = BotName)) +
  coord_polar(start = 0, theta = "y") + 
  scale_fill_manual(values = cbbPalette) +
  xlim(c(0.5, 2.5)) +
  theme_void()
  
# Same information as the donut but perhaps clearer since its ordered
devbot_perc_plot <- ggplot(projects_per_bot, aes(x = reorder(BotName, -Perc), y = Perc)) +
  geom_bar(stat= "identity", color = "white", aes(fill = BotName)) +
  #geom_text()
  geom_text(aes( label = paste(Perc,"%")), vjust = -.5) +
  labs(y = "Percent", fill="DevBots", x = "") +
  scale_fill_manual(values = cbbPalette) +
  PLOT_THEME
devbot_perc_plot
```
